% LaTeX file for resume 

\documentclass{resume} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{fullpage}
%\usepackage[left=2cm, right = 2cm, top = 2cm, bottom = 2cm]{geometry}
%\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor    = blue, %Colour of citations
  naturalnames
}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{bibentry}
%\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{6pt}  % space between header and text
%\setlength{\headheight}{6pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
%\lfoot{\small{P. Blaettchen}} % put text in foot
\lfoot{\small Andres Alban, MGH Institute for Technology Assessment, Sep.\ 2022} % put text in foot
\cfoot{}
\rfoot{\small{\thepage}  } % put text in foot
%\topmargin=-0.7in % start text higher on the page
\renewcommand{\headrulewidth}{0pt}
\newlength{\mylen}
\setbox1=\hbox{$\bullet$}\setbox2=\hbox{\tiny$\bullet$}
\setlength{\mylen}{\dimexpr0.5\ht1-0.5\ht2}
\renewcommand\labelitemi{\raisebox{\mylen}{\tiny$\bullet$}}
\setlength{\parskip}{0.3em}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Andres Alban} % Your name
\address{MGH Institute for Technology Assessment, Harvard Medical School, Boston, MA, USA} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\href{mailto:AALBAN@mgh.harvard.edu}{aalban@mgh.harvard.edu} \textbar\ \href{https://andres-alban.github.io/}{andres-alban.github.io}} % Your phone number and email


\begin{document}

\bibliographystyle{apalike}
\nobibliography{biblio}

\begin{rSection}{Academic Positions}
  \begin{itemize}
    \item Postdoctoral research fellow, MGH Institute for Technology Assessment, Harvard Medical School (2021-present)
  \end{itemize}
\end{rSection}


\begin{rSection}{Education}

\begin{tabular}{lll}
\textbf{Ph.D.} & & INSEAD, Technology and Operations Management (2021)\\
%& & Thesis title\\
\textbf{M.S.} & & INSEAD, M.S. in Management (2018)\\
& & GPA: 3.9\\
\textbf{B.S.} & & New Jersey Institute of Technology, double major in applied mathematics and physics (2016)\\
& & Albert Dorman Honors College, GPA: 4.0
\end{tabular}

\end{rSection}

\begin{rSection}{Research Interests}
My research interests lie broadly in the application of simulation, optimization, and data analysis to support health care decision-making.
% Healthcare operations, clinical trials, personalized medicine, Bayesian optimization, stochastic simulation%, statistical decision theory % optimal learning, decision making under uncertainty
\end{rSection}

\begin{rSection}{Journal Publications}
\begin{itemize}
\item \bibentry{Alban2022}
\item \bibentry{Alban2021}
\item \bibentry{Forster2021}
\item \bibentry{Alban2020b}
\item \bibentry{Alban2017}
\end{itemize}
\end{rSection}

\begin{rSection}{Working papers}
\begin{itemize}
  \item \bibentry{predprog}
\end{itemize}
\end{rSection}

\begin{rSection}{Work in progress}
\begin{itemize}
  \item \bibentry{thyroid_calcitonin}
  \item \bibentry{Fluids}
\end{itemize}
\end{rSection}


\begin{rSection}{Conference proceedings}
\begin{itemize}
\item \bibentry{CovariatesWSC}
\item \bibentry{Alban2020a}
\item \bibentry{Alban2018}
\item \bibentry{Alban2016}
\end{itemize}

\end{rSection}

\begin{rSection}{Conference presentations}

\begin{itemize}
\item Value-based clinical trials: selecting trial lengths and recruitments rates in different regulatory contexts. \textit{INFORMS Annual Meeting 2020, POMS Annual Conference 2021}
\item A value of information approach to designing sequential clinical trials for precision medicine. \textit{INFORMS Annual Meeting 2019, 2020, POMS Annual Conference 2021, INFORMS Healthcare 2021}
\item Fair and efficient? Capacity allocation of mobile family planning services in Uganda. With Philippe Blaettchen, Harwin de Vries, and Luk Van Wassenhove. \textit{INFORMS Annual Meeting 2019}.
\item Personalized Fluid Management in Sepsis Using Transcriptomic Endotypes. With Stephen E. Chick, Spyros I. Zoumpoulis, Brendon P. Scicluna, Fabrice Uhel, and Alexander P.J. Vlaar. \textit{INFORMS Healthcare 2019}.
\item Value-Based Clinical Trial Design to Account for Features of Pragmatic Trials. With Stephen E. Chick and Martin Forster. \textit{POMS Annual Conference 2019}.
\item Extending a Bayesian Decision-Theoretic Approach to Value-Based Sequential Clinical Trials. With Stephen E. Chick and Martin Forster. \textit{Winter Simulation Conference 2018}.
\end{itemize}

\end{rSection}

\begin{rSection}{Grants and Awards}

\begin{itemize}
\item Luk N. Van Wassenhove Ph.D.\ Student Research Award 2019-2020, INSEAD
\item European Sepsis Academy, grant provided by the European Union, 2016-2019
\begin{itemize}
  \item Attended courses on pathogenesis and treatment of sepsis (Amsterdam University Medical Center), diagnostics technologies (BioM\'erieux), immune functional assays (BioM\'erieux), mini MBA (INSEAD), sepsis clinical course (University College London)
\end{itemize}
\item NJIT Provost’s Undergraduate Summer Research program, 2014 and 2015
\item NJIT Albert Dorman Honors College Scholarship
\end{itemize}

\begin{rSection}{Teaching}
\begin{itemize}
\item Process and operations management core class for MBA students (online), INSEAD, Spring 2020
\item Math tutorials for PhD students, INSEAD, Fall 2017.
\item Math tutor and recitation assistant, NJIT Math Tutoring Center, 2013-2016.
\end{itemize}

\end{rSection}


\end{rSection}

\begin{rSection}{Skills}
\begin{itemize}
\item Programming: Julia, Matlab, R, Python, C++, javascript
\item Languages: Spanish (native), English (fluent), German (intermediate), French (basic)
\item Sports: tennis (played NCAA division I at NJIT with scholarship), soccer, ultimate frisbee, touch rugby, basketball
\end{itemize}

\end{rSection}
 
% \begin{rSection}{Recommendation letters}
%   \begin{tabular}{llll}
%     Name & Title & Affiliation & E-mail \\ \hline
%     Stephen E.& Professor of Technology and & INSEAD & \href{mailto:stephen.chick@insead.edu}{stephen.chick@insead.edu} \\
%     Chick & Operations Management \\ \\
%     Martin & Associate Professor of & University of & \href{mailto:martin.forster@unibo.it}{martin.forster@unibo.it} \\
%     Forster & Econimic Statistics & Bologna \\ \\
%     Spyros & Assistant Professor of & INSEAD & \href{mailto:spyros.zoumpoulis@insead.edu}{spyros.zoumpoulis@insead.edu} \\
%     Zoumpoulis & Decision Sciences \\ 
%   \end{tabular}
% \end{rSection}

\end{document}













